Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-06-08 paper.tex
updates

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{figures/Fig7_Fit_eres.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.48\textwidth]{figures/Fig7_eres_40deg.pdf}
}
\caption{ Deduced angular resolutions as functions of (a) photon energy for $\theta=$~10$^{\circ}$ and (b) polar angle for $E_{\gamma}=$~1~GeV. }
\label{fig:angle_reco_dep_gr}
\end{figure}

Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incident photon energy ($E_{\gamma}$) at $\theta=$~25$^{\circ}$. Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively. $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. For small $\theta$, The values are varying up to $\pm$~0.15$^{\circ}$ as shown in Fig.~\ref{fig:angle_reco_dep_gr} (b).

>>>>

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{figures/Fig7_res_ene.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.48\textwidth]{figures/Fig7_Fit_eres.pdf}
}
\caption{ Angular resolutions as functions of the incidence angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$ (b) }
\label{fig:angle_reco_dep_gr}
\end{figure}

Figure~\ref{fig:angle_reco_dep_gr} (a) shows the angular resolution as a function of the incidence angle for different incident energies ($E_{\gamma}$). The angular resolution does not depend on the incidence angle for high incident energy. On the other hand, the angular resolution is especially changing for low incident energy at the small incidence angle. Figure~\ref{fig:angle_reco_dep_gr} (b) shows the angular resolution as a function of the incident photon energy at $\theta=$~25$^{\circ}$. Angular resolutions are fitted with a function of $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$, where $p_{0}$ and $p_{1}$ represent an energy independent and energy dependent contribution, respectively.

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.58\textwidth]{figures/Fig7_eres_40deg.pdf}
\caption{ $p_{1}$ as a function of the incidence angle }
\label{fig:res_edep}
\end{figure}

Figure~\ref{fig:res_edep} shows estimated $p_{1}$ as a function of the incidence angle. $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. For small $\theta$, $p_{1}$ is smaller than larger $\theta$ as the angular resolution is significantly dependent on the incidence angle for the low incident energy.
